---
title: "p8105_hw2_dx2262"
output: html_document
---

```{r}
library(tidyverse)
library(readxl)
```


## Problem 2

Load the dataset

Mr. Trash Wheel:
```{r}
Mr_df <- 
  read_excel("data/202509 Trash Wheel Collection Data.xlsx", 
             sheet = 1, 
             skip = 1, 
             na = c("NA", ".", "")) %>% 
  janitor::clean_names() %>% 
  select(-x15, -x16) %>% 
  mutate(sports_balls = as.integer(round(sports_balls, 0)),
         wheel = "mr",
         year = as.numeric(year)) %>% 
  relocate(wheel, everything())
  
```

Professor Trash Wheel:
```{r}
Prof_df <- 
  read_excel("data/202509 Trash Wheel Collection Data.xlsx", 
             sheet = 2, 
             skip = 1, 
             na = c("NA", ".", "")) %>% 
  janitor::clean_names() %>% 
  mutate(wheel = "prof",
         year = as.numeric(year)) %>% 
  relocate(wheel, everything())
```

Gwynns:
```{r}
GF_df <- 
  read_excel("data/202509 Trash Wheel Collection Data.xlsx", 
             sheet = 4, 
             skip = 1, 
             na = c("NA", ".", "")) %>% 
  janitor::clean_names() %>% 
  mutate(wheel = "gwynns",
         year = as.numeric(year)) %>% 
  relocate(wheel, everything())
```

Combine datasets

```{r}
TrashWheel_df <- bind_rows(Mr_df, Prof_df, GF_df)
```

The total number of observations in the resulting dataset is 1191.

Key variables are `r paste(names(TrashWheel_df), collapse = ", ")`.

The total weight of trash collected by Professor Trash Wheel is `r Prof_df %>% pull(weight_tons) %>% sum(na.rm = TRUE)`

The total number of cigarette butts collected by Gwynns in June of 2022 is `r GF_df %>% filter(year == 2022, month == "June") %>% pull(cigarette_butts) %>% sum(na.rm = TRUE)`.


## Problem 3















Create a single, well-organized dataset with all the information contained in these data files. To that end: import, clean, tidy, and otherwise wrangle each of these datasets; check for completeness and correctness across datasets (e.g. by viewing individual datasets and monitoring warning messages); merge to create a single, final dataset; and organize this so that variables and observations are in meaningful orders.

Briefly describe the resulting tidy dataset. How many total observations exist? How many unique ZIP codes are included, and how many unique neighborhoods?

Which ZIP codes appear in the ZIP code dataset but not in the Zillow Rental Price dataset? Using a few illustrative examples discuss why these ZIP codes might be excluded from the Zillow dataset.

Rental prices fluctuated dramatically during the COVID-19 pandemic. For all available ZIP codes, compare rental prices in January 2021 to prices in January 2020. Make a table that shows the 10 ZIP codes (along with the borough and neighborhood) with largest drop in price from January 2020 to 2021. Comment.


